Many symmetric monoidal categories $\cat{C}$ have the property that each object $c\in\cat{C}$ is equipped with a certain algebraic structure---say that of a monoid or a comonoid---in a way that is compatible with $\cat{C}$'s monoidal structure.

For example, consider the category $\rel$ of relations between sets. It has a symmetric monoidal structure $(I, \otimes, \gamma)$ coming from the cartesian monoidal structure of $\smset$. This is not a cartesian monoidal structure on $\rel$: indeed, $I$ is not terminal. And yet each object $r\in\rel$ is equipped with morphisms $\delta_r\colon r\to r\otimes r$ and $\epsilon_r\colon r\to I$, which satisfy the same \emph{algebraic} properties that a diagonal and a terminal morphism do. Namely, the diagrams expressing commutativity, unitality, and associativity commute:
The main theorems of this paper are that supply and supply preservation are
well-behaved with respect to coherence isomorphisms. In we show that every
associator and unitor in $\cat{C}$ is automatically a homomorphism for any
supply. In we show that the coherence isomorphisms for strong monoidal functors
$F\colon\cat{C}\to\cat{D}$ are automatically homomorphisms whenever $F$
preserves the supply. We give strictification theorems. 

 
% Subsection %
\paragraph{\temph{Acknowledgements.}}
We thank Dmitry Vagner for interesting and useful conversations. We also thank
Tobias Fritz for catching an error in a draft and for suggesting the
strictification theorem which he had previously proven independently \ref{hello} in
a special case and shared with us; see \cite{spivak_poly_2020} forthcoming.
We acknowledge support from Honeywell Inc., and from AFOSR grants FA9550-17-1-0058 and FA9550-19-1-0113.
